---
title: "HW8"
author: "Erin Ferranti"
date: "4/11/2018"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

K-nearest neighbor

Let's try a variation on the NHANES data set again.

```{r}
library(tidyverse)
library(class)
library(rpart)
library(NHANES)
library(RColorBrewer)
library(plot3D)
library(parallel)
library(randomForestSRC)
library(ggRandomForests)
library(mosaic)

# Create the NHANES dataset again
```

Create the NHANES dataset again, just like we did in class, only using sleep trouble (variable name = SleepTrouble) as the dependent variable, instead of SleepTrouble. 

####Problem 1

What is the marginal distribution of sleep trouble?

```{r}
people <- NHANES %>% dplyr::select(Age, Gender, SleepTrouble, BMI, HHIncome, PhysActive) 
#%>% na.omit()

glimpse(people)


tally(~ SleepTrouble, data = people, format = "percent")
#Insert your code here to determine the marginal distribution of sleep trouble in the NHANES dataset.

```

Recall from our prior work, the packages work better if the dataset is a dataframe, and the variables are numeric.



```{r}
class(people)

# Convert back to dataframe
people <- as.data.frame(people)
glimpse(people)

# Convert factors to numeric - the packages just seem to work better that way
people$Gender <- as.numeric(people$Gender)
people$SleepTrouble <- as.numeric(people$SleepTrouble)
people$HHIncome <- as.numeric(people$HHIncome)
people$PhysActive <- as.numeric(people$PhysActive)

people <- na.omit(people)

glimpse(people)


```

Apply the k-nearest neighbor procedure to predict SleepTrouble from the other covariates, as we did for SleepTrouble. Use k = 1, 3, 5, and 20.

####Problem 2

```{r}

knn.1 <- knn(train = people, test = people, cl = as.numeric(people$SleepTrouble), k = 1)
knn.3 <- knn(train = people, test = people, cl = people$SleepTrouble, k = 3)
knn.5 <- knn(train = people, test = people, cl = people$SleepTrouble, k = 5)
knn.20 <- knn(train = people, test = people, cl = people$SleepTrouble, k = 20)


```

Now let's see how well these classifiers work overall

####Problem 3

```{r}
100*sum(people$SleepTrouble == knn.1)/length(knn.1)
100*sum(people$SleepTrouble == knn.3)/length(knn.3)
100*sum(people$SleepTrouble == knn.5)/length(knn.5)
100*sum(people$SleepTrouble == knn.20)/length(knn.20)
# How well do these classifiers (k = 1, 3, 5, 20) work?
# Insert your code here


```

####Problem 4

What about success overall?

```{r}
table(knn.1, people$SleepTrouble)
table(knn.3, people$SleepTrouble)
table(knn.5, people$SleepTrouble)
table(knn.20, people$SleepTrouble)
#Insert your code here to determine overall success for k = 1, 3, 5, 20

```


